---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tab10

<!-- badges: start -->
<!-- badges: end -->

The goal of `tab10` is to support risk communication. Many people struggle with the interpretation of probability. This package develops a new interactive graphical instrument, the **Table of Ten**, to ease gaining insight into personal risk probabilities. The goals of the method are to communicate

1. the prevalence of a future outcome;
2. the rank of the person's predicted probability relative to other people;
3. the positive predictive value of the prediction;
4. the effect of "doing something" versus "doing nothing".

Not every goal has yet been achieved. Most of the developments in the present package relate to points 1, 2 and 3.

## Installation

You can install the development version of tab10 like so:

```{r eval=FALSE}
remotes::install_github("growthcharts/tab10")
```

## Example overweight

This is a basic example to communicate the probability of getting overweight at the age of 4 years, given data of infants aged 6-12 months.

```{r overweight, fig.retina=2}
library(tab10)
fig <- create_tab10(palet = "redgrey")
fig
```

GitHub README does not allow animation. Install and run the above code locally.

## Example preterm birth (GA < 37 weeks)

```{r preterm, fig.retina=2}
library(tab10)
fig <- create_tab10(name = "preterm-37w-1", palet = "redgrey")
fig
```


